Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex

>>>>

\end{document}
=======
\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{url}
\newcommand{\kai}[1]{{\bf \color{blue} [[Shukai says ``#1'']]}}
\newcommand{\heng}[1]{{\bf \color{cyan} [[Yuheng says ``#1'']]}}
\newcommand{\hao}[1]{{\bf \color{red} [[Hao says ``#1'']]}}
\newcommand{\hui}[1]{{\bf \color{purple} [[Zhenghui says ``#1'']]}}
% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\begin{document}
	\title{Predicting Internet Path Dynamics and Performance with Machine Leanring}
	%\titlenote{Produces the permission block, and
	%  copyright information}
	%\subtitle{Extended Abstract}
	%\subtitlenote{The full version of the author's guide is available as
	%  \texttt{acmart.pdf} document}

	\maketitle
	\hui{I think we should focus on the process not the final result, which is also important.}
	\section{Introduction}
	1. introduce the original paper: their task, method, and dataset
	Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures. Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity. Thus, it is of great significant to predict Internet path dynamics and performance.

	In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements. They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths. Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

	To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction. Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.

	The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open
	Internet measurement initiative. The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers. However, most of the paths are not periodically sampled during this week. And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week. So the dataset only contains corresponding infomation of these 2,346 paths.

	We find some drawbacks in their data process.
	The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.

	\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}

	And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results. Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.

	\section{Related Works}
	1. introduce the original paper
	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

	And to achieve these three targets, 69 input features are used to describe the  statistical properties of route dynamics and path latency.
	For the first route dynamic target, the first group of 11 features,referred to as $F_A$, is chosen. It describes the statistical properties (average, minimum, maximum, and percentiles) of the route duration observed for each path.
	And for the second target, the second group of 14 features, as $F_B$, are relevant to the prediction of number of route changes. $F_B$ features take into account the statistical properties of route changes. In addition to that, $F_B$ contains information about the number of route changes observed for a path so far and a binary feature indicating whether a route change occurred for a path in the current time slot. 
	And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement. They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.

	Then they study the correlation among the input features and the targets and apply  feature selection techniques to select the best features for prediction. When using as input the full set of 69 input features $F_A \cup F_B \cup F_C$, and perform wrapper-based feature selection on top of this full set. The result shows that the top important features for three targets are not necessarily the ones in corresponding $F_A,F_B$ or $F_C$.

	And the authors use three different ways of selecting input features: $(i)$  use all of the 69 features to predict each target, $(ii)$ when predicting target $X$, use corresponding feature set $F_X$, $(iii)$ after wrapper-based feature selection, use the top features for each target. And finally, what they get is the third way of choosing input features can achieve better results (though there is only minor differences in output results).

	\section{Data Analysis}
	\hui{I think this is a important part, who will take this part?}
